Whole-chromosome pairwise alignment using a hierarchical wavefront algorithm

### 2021-05-31 manuscript/main.tex
added Data availability

>>>>

    \vspace*{+12pt}
    \textit{Financial Support}: none declared.

    \textit{Conflict of Interest}: none declared.
    \vspace*{+12pt}

    \section*{Data availability}

    Data used for the simulations is available at \href{https://github.com/marbl/CHM13}{https://github.com/marbl/CHM13}.
    Data used for Human pangenome graph analysis is available at \href{https://github.com/human-pangenomics/HPP_Year1_Data_Freeze_v1.0}{https://github.com/human-pangenomics/HPP\_Year1\_Data\_Freeze\_v1.0}.

    \section*{Acknowledgements}
    %ToDo
    XXXXXXX XXXXXXXX XXXXXXXX XXXXXXXX XXXXXXXX XXXXXXXX XXXXXXXX XXXXXXXX XXXXXXXX.

    \section*{Funding}
    %ToDo
    This work has been supported by the XXXXXXXX XXXXXXXX XXXXXXXX XXXXXXXX XXXXXXXX.
